An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-03-29 EconGrowthSeminar.Rnw
Changed nomenclature on country groups. Now including slides for Caleb's energy information.

\begin{frame}{Type of Economy} %----------------------------
  \begin{center}
    \begin{tabular}{r c c l}
      \multirow{3}{*}{Developed}  & \includegraphics[height=0.11in]{flag/flag_US.png} & US & USA           \\
                                  & \includegraphics[height=0.11in]{flag/flag_UK.png} & UK & United Kingdom\\
                                  & \includegraphics[height=0.11in]{flag/flag_JP.png} & JP & Japan         \\
      \hline
      \multirow{2}{*}{Developing} & \includegraphics[height=0.11in]{flag/flag_CN.png} & CN & China         \\
                                  & \includegraphics[height=0.11in]{flag/flag_ZA.png} & ZA & South Africa  \\
      \hline
      \multirow{2}{*}{Petrol}     & \includegraphics[height=0.11in]{flag/flag_SA.png} & SA & Saudi Arabia  \\
                                  & \includegraphics[height=0.11in]{flag/flag_IR.png} & IR & Iran          \\
      \hline
      \multirow{2}{*}{Malthusian} & \includegraphics[height=0.11in]{flag/flag_TZ.png} & TZ & Tanzania      \\
                                  & \includegraphics[height=0.11in]{flag/flag_ZM.png} & ZM & Zambia        \\
    \end{tabular}
  \end{center}
\end{frame}

@@

\begin{frame}{Economic Data: Definitions} %----------------------------
  \begin{itemize}
    \item{Output ($Y$): the real market value of the total amount of produced goods in an economy (GDP).}
    \item{Capital Stock ($K$): the real market value of the total amount of goods in an economy used in the production process of output (machines, tools, infrastructure, etc.).}
    \item{Labor: the number of workers in an economy that produce output. Labor can be treated as either the total number of workers in an economy or the total number of hours worked per year in an economy.}
  \end{itemize}
\end{frame}

\begin{frame}{Sources of Economic Data} %----------------------------
  \begin{center}
    \tiny
    \begin{tabular}{r c|c l}
      \multirow{3}{*}{WB GEP} & \multirow{3}{*}{\includegraphics[scale=0.07]{figure_other/Figure_World_Bank.png}} & $Y$, $K$ for all countries & \multirow{3}{*}{Real 2005\$} \\
                              &                          & (1980-2011: US, UK, JP; & \\
                              &                          & 1991-2011: CN, ZA, SA, IR, TZ, ZM) & \\
      \hline
      \multirow{4}{*}{WB WDI} & \multirow{4}{*}{\includegraphics[scale=0.07]{figure_other/Figure_World_Bank.png}} & Pop, Pop < 15 yo,    & \multirow{4}{*}{Total Employment} \\
                              &                          & Emp/Pop ratio > 15 yo, &                                \\
                              &                          & used to find $L$, (1991-2011: &                         \\
                              &                          & CN, ZA, SA, IR, TZ, ZM) &                         \\
      \hline
      \multirow{2}{*}{US BLS} & \multirow{2}{*}{\includegraphics[scale=0.07]{figure_other/Figure_BLS.png}} & $L$ for developed countries & Labor hours \\
                              &                          & (1980-2011: US, UK, JP)     & per year \\ 
    \end{tabular}
  \normalsize
  \end{center}
\end{frame}

@@

\begin{frame}{Energy Data} %----------------------------
  Caleb complete
\end{frame}

>>>>

\begin{frame}{Type of Economy} %----------------------------
  \begin{center}
    \begin{tabular}{r c c l}
      \multirow{3}{*}{Developed}  & \includegraphics[height=0.11in]{flag/flag_US.png} & US & USA           \\
                                  & \includegraphics[height=0.11in]{flag/flag_UK.png} & UK & United Kingdom\\
                                  & \includegraphics[height=0.11in]{flag/flag_JP.png} & JP & Japan         \\
      \hline
      \multirow{2}{*}{BRICS}      & \includegraphics[height=0.11in]{flag/flag_CN.png} & CN & China         \\
                                  & \includegraphics[height=0.11in]{flag/flag_ZA.png} & ZA & South Africa  \\
      \hline
      \multirow{2}{*}{Petrol}     & \includegraphics[height=0.11in]{flag/flag_SA.png} & SA & Saudi Arabia  \\
                                  & \includegraphics[height=0.11in]{flag/flag_IR.png} & IR & Iran          \\
      \hline
      \multirow{2}{*}{LDCs}       & \includegraphics[height=0.11in]{flag/flag_TZ.png} & TZ & Tanzania      \\
                                  & \includegraphics[height=0.11in]{flag/flag_ZM.png} & ZM & Zambia        \\
    \end{tabular}
  \end{center}
\end{frame}

@@

\begin{frame}{Economic Data: Definitions} %----------------------------
  \begin{itemize}
    \item{Output ($Y$): the real market value of the total amount of produced goods in an economy (GDP).}
    \item{Capital Stock ($K$): the real market value of the total amount of goods in an economy used in the production process of output (machines, tools, infrastructure, etc.).}
    \item{Labor ($L$): the number of workers in an economy that produce output. Labor can be treated as either the total number of workers in an economy or the total number of hours worked per year in an economy.}
  \end{itemize}
\end{frame}

\begin{frame}{Sources of Economic Data} %----------------------------
  \begin{center}
    \scriptsize
    \begin{tabular}{r c|c l}
      \multirow{3}{*}{WB GEP} & \multirow{3}{*}{\includegraphics[scale=0.07]{figure_other/Figure_World_Bank.png}} & $Y$, $K$ for all countries & \multirow{3}{*}{Real 2005\$} \\
                              &                          & (1980-2011: US, UK, JP; & \\
                              &                          & 1991-2011: CN, ZA, SA, IR, TZ, ZM) & \\
      \hline
      \multirow{4}{*}{WB WDI} & \multirow{4}{*}{\includegraphics[scale=0.07]{figure_other/Figure_World_Bank.png}} & Pop, Pop < 15 yo,    & \multirow{4}{*}{Total Employment} \\
                              &                          & Emp/Pop ratio > 15 yo, &                                \\
                              &                          & used to find $L$, (1991-2011: &                         \\
                              &                          & CN, ZA, SA, IR, TZ, ZM) &                         \\
      \hline
      \multirow{2}{*}{US BLS} & \multirow{2}{*}{\includegraphics[scale=0.07]{figure_other/Figure_BLS.png}} & $L$ for developed countries & Labor hours \\
                              &                          & (1980-2011: US, UK, JP)     & per year \\ 
    \end{tabular}
  \normalsize
  \end{center}
\end{frame}

@@

\begin{frame}{Energy Data: Definitions} %----------------------------
  \begin{itemize}
    \item{Thermal Energy ($Q$): The heat content of an energy carrier.}
    \item{Exergy ($X$): The maximum work that can be extracted from a heat carrier by a process that brings the system into equillibrium with a thermal reservoir (typically the surrounding environment).}
    \item{Useful Work ($U$): Energy that directly generates economic activity.}
  \end{itemize}
\end{frame}

\begin{frame}{Energy Flows} %----------------------------
  Caleb's diagram here
\end{frame}

\begin{frame}{Sources of Energy Data} %----------------------------
  Table here.
\end{frame}
